% prelude.tex
%   - titlepage
%   - dedication
%   - acknowledgments
%   - table of contents, list of tables and list of figures
%   - nomenclature
%   - abstract
%============================================================================


\clearpage\pagenumbering{roman}  % This makes the page numbers Roman (i, ii, etc)



% TITLE PAGE
%   - define \title{} \author{} \date{}
\title{Integration of control theory and scheduling methods for supply
  chain management}
\author{Kaushik Subramanian}
\date{2013}
%   - The default degree is ``Doctor of Philosophy''
%     (unless the document style msthesis is specified
%      and then the default degree is ``Master of Science'')
%     Degree can be changed using the command \degree{}
%\degree{Master \TeX nician}
%   - The default is dissertation, unless the document style
%     msthesis was specified in which case it becomes thesis.
%     If msthesis is specified for the MS margins, you can
%     still have a dissertation if you specify \disseration
%\disseration
%   - for a masters project report, specify \project
%\project
%   - for a preliminary report, specify \prelim
%\prelim
%   - for a masters thesis, specify \thesis
%\thesis
%   - The default department is ``Electrical Engineering''
%     The department can be changed using the command \department{}
\department{Chemical and Biological Engineering}
%   - once the above are defined, use \maketitle to generate the titlepage
\maketitle

% COPYRIGHT PAGE
%   - To include a copyright page use \copyrightpage
\copyrightpage

% DEDICATION
\begin{dedication}
To my teachers.
\end{dedication}

% ACKNOWLEDGMENTS
\begin{acknowledgments}
I would like to express my sincere thanks to my advisers, Prof Jim
Rawlings and Prof. Christos Maravelias for their invaluable help and
guidance. Their depth of knowledge, attention to detail, and
enthusiasm to teach and learn has always motivated me. 

I would like to thank Prof Scahin Patwardhan, for his invaluable
advice and guidance regarding my decision to pursue a PhD.
 
I also thank Prof. Ross Swaney, Prof. Jennifer Reed, Prof. Michael
Graham and Prof. Ananth Krishnamurthy for taking time to be on my
thesis committee.
  
I would like to thank Dr Jesus Flores-Cerrillo and Dr Lawrence Megan
from the Advanced Controls and Optimizations group at Praxair,
Tonawanda, NY, for giving me the opportunity to work in an exciting
industrial research group. I have returned brimming with new ideas
after my visits to Praxair. 

I would like to thank Dr Aswin Venkat and Brent Miller from Bloom
Energy. The experience working in a start-up company is truly unique.

I would like to thank all the members of Jim Rawlings' group. 
It is always a pleasure interacting with Ankur
Gupta, may it be about optimization algorithms or about the Lannister
clan. Rishi Srivastava has been a very good and patient friend. I
enjoyed my time with  Brett Stewart, whose guidance helped me a lot in 
understanding  my research problem. Rishi Amrit has been a savior
whenever I experienced computing troubles. His help in explaining
Economic MPC to me has helped me immensely. I have also enjoyed
interacting with Cuyler Bates, who has listened patiently to all my new
ideas. I must thank Mary Diaz, for all her administrative support and the delicious
cookies and cakes.

I am also thankful to all the friends I have made in Madison. The
memories with Swami, Raghu, Sriram, Pavithra, Janani are something
that I shall cherish for the rest of my life. 

Thanks to the ``Panni group'' - Sashi, Shriram, Srikant, Anand. I look
forward to many more New year ``reunion'' trips!

Finally,  a big thanks to Amma, Appa and, Vidu for all their love,
encouragement and support.
  
  \raggedleft
  Kaushik - Madison, WI

\end{acknowledgments}

% CONTENTS, TABLES, FIGURES
\tableofcontents
\listoftables
\listoffigures

% NOMENCLATURE
%\input{notation}



\advisorname{James B.\ Rawlings \&  Christos T.\ Maravelias}
\advisortitle{Professors}
% ABSTRACT


\begin{abstract}
  \input{abstract}
\end{abstract}


\clearpage\pagenumbering{arabic} % This makes the page numbers Arabic (1, 2, etc)
